The Influence of Connectivity on Dung Beetle Communities

### 2025-08-02 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
im sleepy

# output: bookdown::pdf_document2
  # pdf_document:
  #   includes:
  #     # in_header: style/preamble.tex
  #     template: null
  #     keep_tex: no
  #     extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

>>>>

#output: bookdown::pdf_document2
#pdf_document:
#  includes:
    # in_header: style/preamble.tex
#    template: null
#    keep_tex: no
#    extra_dependencies: ["float"]
#    number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

```{r, label = abund-bmass, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Trendline of average dung beetle biomass by total individuals captured.", out.width="70%", fig.align='center'}

knitr::include_graphics("images/bmass_v_abund.png")
```
